Brain Tumor Detection using Machine Learning Models

### 2021-08-04 slides.tex
added acknowledgement

\author[Rajarshi, Bhargav, Soptorshi, Brahmajit] {
	Bhargav Basu (183313-21-0045) \texorpdfstring{\\} \and
	Soptorshi Bhattacharjee (183313-21-0050) \texorpdfstring{\\} \and
	Brahmajit Das (183313-21-0044) \texorpdfstring{\\} \and
	Rajarshi Sardar (183313-21-0055)
}

@@

	\begin{frame}
		\frametitle{Overview}
		\begin{columns}[totalwidth=0.9\textwidth]
			\hspace*{2.5cm}
			\begin{column}{0.35\textwidth}
				\tableofcontents[sections={1-4}]
			\end{column}
			\begin{column}{0.35\textwidth}
				\tableofcontents[sections={5-9}]
			\end{column}
		\end{columns}
	\end{frame}

@@

>>>>

\author[Rajarshi, Bhargav, Soptorshi, Brahmajit] {
	Bhargav Basu (183313-21-0045) \texorpdfstring{\\} \and
	Soptorshi Bhattacharjee (183313-21-0050) \texorpdfstring{\\} \and
	Brahmajit Das (183313-21-0044) \texorpdfstring{\\} \and
	Rajarshi Sardar (183313-21-0055) \texorpdfstring{\\ \vspace{1cm}} \and
	Project Guide: Prof. \textbf{Kajari Bhattacharjee}
}

@@

	\begin{frame}
		\frametitle{Overview}
		\begin{columns}[totalwidth=0.9\textwidth]
			\hspace*{2.5cm}
			\begin{column}{0.35\textwidth}
				\tableofcontents[sections={1-5}]
			\end{column}
			\begin{column}{0.35\textwidth}
				\tableofcontents[sections={6-10}]
			\end{column}
		\end{columns}
	\end{frame}

@@

	\section{Acknowledgement}

	\begin{frame}
		\frametitle{Acknowledgement}

		We take this opportunity to express profound sense of gratitude and respect to
		all those who helped us throughout the duration of this project.

		First and foremost, We would like to thank my supervisor of this project, Prof.
		\textbf{Kajari Bhattacharjee}, for her valuable time and guidance. Her
		willingness to motivate me has contributed tremendously to my project.

		We would also like to thank Prof. \textbf{Srijeeta Chakrabarti}, Head of
		Department of Computer Science, for providing with a good environment and
		facilities to work on this project.
	\end{frame}
